---
title: "Movies Analysis"
author: "Francisco Castillo, Fernanda Esquivel y Andrés Montoya"
date: "29/01/2024"
output:
  html_document:
    df_print: paged
---
Investigue si las variables cuantitativas siguen una distribución normal y haga una tabla de frecuencias de las variables cualitativas.
## Variables cuantitativas
```{r}
movies <- read.csv("movies.csv")
summary(movies)
if (!requireNamespace("knitr", quietly = TRUE)) {
  install.packages("knitr")
}
library(knitr)
```
### Budget
```{r}
hist(movies$budget, col = "lightblue", main = "Budget", xlab = "Budget")
```
### Revenue 
```{r}
hist(movies$revenue, col = "lightblue", main = "Revenue", xlab = "Revenue")
```
### Runtime
```{r}
hist(movies$runtime, col = "lightblue", main = "Runtime", xlab = "Runtime")
```
### Popularity
```{r}
hist(movies$popularity, col = "lightblue", main = "Popularity", xlab = "Popularity")
```
### Vote Average
```{r}
hist(movies$voteAvg, col = "lightblue", main = "Vote Average", xlab = "Vote Average")
```
### Vote Count
```{r}
hist(movies$voteCount, col = "lightblue", main = "Vote Count", xlab = "Vote Count")
```
### Genres Amount
```{r}
hist(movies$genresAmount, col = "lightblue", main = "Genres Amount", xlab = "Genres Amount")
```
### Production Companies Amount
```{r}
hist(movies$productionCoAmount, col = "lightblue", main = "Production Companies Amount", xlab = "Production Companies Amount")
```
### Production Countries Amount
```{r}
hist(movies$productionCountriesAmount, col = "lightblue", main = "Production Countries Amount", xlab = "Production Countries Amount")
```
### Actors Amount
```{r}
hist(movies$actorsAmount, col = "lightblue", main = "Actors Amount", xlab = "Actors Amount")
```
### Cast Women Amount
```{r}
movies$int_cast_women_amount <- as.integer(movies$castWomenAmount)
hist(movies$int_cast_women_amount, col = "lightblue", main = "Cast Women Amount", xlab = "Cast Women Amount")
```
### Cast Men Amount
```{r}
movies$int_cast_men_amount <- as.integer(movies$castMenAmount)
hist(movies$int_cast_men_amount, col = "lightblue", main = "Cast Men Amount", xlab = "Cast Men Amount")
```

## Variables cualitativas
### Genres
```{r}
split_genres <- strsplit(movies$genres, "|", fixed = TRUE)
genres <- unlist(split_genres)
genres_freq <- table(genres)
genres_freq_table <- as.data.frame(genres_freq)
colnames(genres_freq_table) <- c("Genres", "Frequency")
print(genres_freq_table)
```
### Production Companies
```{r}
split_prod_company <- strsplit(movies$productionCompany, "|", fixed = TRUE)
prod_company <- unlist(split_prod_company)
prod_company_freq <- table(prod_company)
prod_company_freq_table <- as.data.frame(prod_company_freq)
colnames(prod_company_freq_table) <- c("Production Companies", "Frequency")
print(tail(prod_company_freq_table, n = 10))
```
### Production Company Countries
```{r}
split_prod_company_country <- strsplit(movies$productionCompanyCountry, "|", fixed = TRUE)
prod_company_country <- unlist(split_prod_company_country)
prod_company_country_freq <- table(prod_company_country)
prod_company_country_freq_table <- as.data.frame(prod_company_country_freq)
colnames(prod_company_country_freq_table) <- c("Production Companies Countries", "Frequency")
print(head(prod_company_country_freq_table, n = 10))
```
### Production Countries
```{r}
split_prod_country <- strsplit(movies$productionCountry, "|", fixed = TRUE)
prod_country <- unlist(split_prod_country)
prod_country_freq <- table(prod_country)
prod_country_freq_table <- as.data.frame(prod_country_freq)
colnames(prod_country_freq_table) <- c("Production Countries", "Frequency")
print(head(prod_country_freq_table, n = 10))
```
### Video
```{r}
video_freq <- table(movies$video)
video_freq_table <- as.data.frame(video_freq)
colnames(video_freq_table) <- c("Video", "Frequency")
print(video_freq_table)
```
### Director
```{r}
split_director <- strsplit(movies$director, "|", fixed = TRUE)
director <- unlist(split_director)
director_freq <- table(director)
director_freq_table <- as.data.frame(director_freq)
colnames(director_freq_table) <- c("Director", "Frequency")
print(tail(director_freq_table, n = 10))
```
### Original Language
```{r}
original_language_freq <- table(movies$originalLanguage)
original_language_freq_table <- as.data.frame(original_language_freq)
colnames(original_language_freq_table) <- c("Original Language", "Frequency")
print(original_language_freq_table)
```
### Release Date
```{r}
release_date_freq <- table(movies$releaseDate)
release_date_freq_table <- as.data.frame(release_date_freq)
colnames(release_date_freq_table) <- c("Release Date", "Frequency")
print(head(release_date_freq_table, n = 10))
```

